DATA 621 - Final Project

### 2019-11-05 final project/Final_Project.Rmd
Update final

---
title: "DATA 621 - Final Project"
author: "Critical Thinking Group 3"
date: "`r Sys.Date()`"
output: html_document
---

@@

## Abstract

Use 250 words or less to summarize your problem, methodology, and major outcomes.

**Key Words: Regression**

>>>>

---
title: "DATA 621 - Final Project"
author:
  - name: Corey Arnouts
    affiliation: CUNY School of Professional Studies
  - name: Adam Douglas
    affiliation: CUNY School of Professional Studies
  - name: Jason Givens-Doyle
    affiliation: CUNY School of Professional Studies
  - name: Michael Silva
    affiliation: CUNY School of Professional Studies
    email: Michael.Silva39@spsmail.cuny.edu
date: "`r Sys.Date()`"
output:
  html_document: default
  rticles::asa_article:
    citation_package: natbib
    keep_tex: yes
    number_sections: no
    toc: no
keywords: keywordA, keywordB
abstract: Use 250 words or less to summarize your problem, methodology, and major outcomes. \newline This is the second line of abstract.
---

@@
